Concurrent Programming with CXL

### 2020-06-15 book/paper.tex
Made figures more clear
Add non-blocking queue a la Herlihy/Wing

\begin{figure}
\begin{center}
\includegraphics[width=4in]{figures/mutex.jpeg}
\end{center}
\caption{High-level state diagram specification of mutual exclusion with up to two processes.
The first number in a state gives the number of processes; the second number is the
number of processes in the critical section.}
\label{fig:mutex}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=4in]{figures/states.jpeg}
\end{center}
\caption{Venn diagram of all states and a trace.}
\label{fig:states}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=2in]{figures/rdwr.jpeg}
\end{center}
\caption{High-level state diagram specification of reader/writer locks with
up to two processes.
The first number in a state gives the number of processes; the second number is the
number of processes reading in the critical section; the third is the number of
processes writing in the critical section.}
\label{fig:rdwr}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=2.5in]{figures/pc.jpeg}
\end{center}
\caption{High-level state diagram specification of producers/consumers.}
\label{fig:pc}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=6in]{figures/monitor.jpeg}
\end{center}
\caption{High-level depictions of Hoare and Mesa monitors.  The hall is
where processes wait to enter the bathroom (the critical section).  The
bedrooms illustrate two condition variables.  The circles are processes.}
\label{fig:monitors}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{figures/barrier.jpeg}
\end{center}
\caption{High-level state diagram specification of barrier synchronization
with three processes and three rounds.  The three numbers specify the round
number of each process.}
\label{fig:barrierdiagram}
\end{figure}

@@

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
\texttt{e == e} & any two CXL values \\
\hline
\texttt{e != e} & any two CXL values \\
\hline
\texttt{e < e} & any two CXL values \\
\hline
\texttt{e <= e} & any two CXL values \\
\hline
\texttt{e > e} & any two CXL values \\
\hline
\texttt{e >= e} & any two CXL values \\
\hline
\texttt{e and e and ...} & two or more Booleans \\
\hline
\texttt{e or e or ...} & two or more Booleans \\
\hline
\texttt{not e} & a Boolean \\
\hline
\texttt{-e} & an integer \\
\hline
\texttt{e + e + ...} & two or more integers, sets, or lists \\
\hline
\texttt{e - e} & two integers or sets \\
\hline
\texttt{e * e * ...} & two or more integers or sets \\
\hline
\texttt{e / e} & two integers (integer division) \\
\hline
\texttt{e \% e} & two integers (division remainder) \\
\hline
\texttt{e~..~e} & two integers \\
\hline
\texttt{e in e} & first is any CXL value, second is set \\
\hline
\texttt{e not in e} & first is any CXL value, second is set \\
\hline
\texttt{e if e else e} & middle \texttt{e} must be a Boolean \\
\hline
\texttt{\^{}e} & an address \\
\hline
\texttt{choose e} & a set \\
\hline
\texttt{min e} & a set \\
\hline
\texttt{max e} & a set \\
\hline
\texttt{cardinality e} & a set \\
\hline
\texttt{keys e} & a dictionary \\
\hline
\texttt{len e} & a dictionary (includes tuple or list) \\
\hline
\texttt{bagsize e} & a bag \\
\hline
\texttt{atLabel e} & atom (corresponding to a label) \\
\hline
\texttt{nametag e} & \texttt{e} must be \texttt{()} \\
\hline
\texttt{processes e} & \texttt{e} must be \texttt{()} \\
\hline
\texttt{\&(lv)} & \texttt{lv} is an lvalue \\
\hline
\texttt{stop lv} & \texttt{lv} is an lvalue \\
\hline
\end{tabular}
\vspace{1em}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=4in]{figures/mutex-crop.pdf}
\end{center}
\caption{High-level state diagram specification of mutual exclusion with up to two processes.
The first number in a state gives the number of processes; the second number is the
number of processes in the critical section.}
\label{fig:mutex}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=4in]{figures/states-crop.pdf}
\end{center}
\caption{Venn diagram of all states and a trace.}
\label{fig:states}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=2in]{figures/rdwr-crop.pdf}
\end{center}
\caption{High-level state diagram specification of reader/writer locks with
up to two processes.
The first number in a state gives the number of processes; the second number is the
number of processes reading in the critical section; the third is the number of
processes writing in the critical section.}
\label{fig:rdwr}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=2.5in]{figures/pc-crop.pdf}
\end{center}
\caption{High-level state diagram specification of producers/consumers.}
\label{fig:pc}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=6in]{figures/monitor-crop.pdf}
\end{center}
\caption{High-level depictions of Hoare and Mesa monitors.  The hall is
where processes wait to enter the bathroom (the critical section).  The
bedrooms illustrate two condition variables.  The circles are processes.}
\label{fig:monitors}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{figures/barrier-crop.pdf}
\end{center}
\caption{High-level state diagram specification of barrier synchronization
with three processes and three rounds.  The three numbers specify the round
number of each process.}
\label{fig:barrierdiagram}
\end{figure}

@@

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
\texttt{e == e} & two CXL values of the same type \\
\hline
\texttt{e != e} & two CXL values of the same type \\
\hline
\texttt{e < e} & any two CXL values \\
\hline
\texttt{e <= e} & any two CXL values \\
\hline
\texttt{e > e} & any two CXL values \\
\hline
\texttt{e >= e} & any two CXL values \\
\hline
\texttt{e and e and ...} & two or more Booleans \\
\hline
\texttt{e or e or ...} & two or more Booleans \\
\hline
\texttt{not e} & a Boolean \\
\hline
\texttt{-e} & an integer \\
\hline
\texttt{e + e + ...} & two or more integers, sets, or lists \\
\hline
\texttt{e - e} & two integers or sets \\
\hline
\texttt{e * e * ...} & two or more integers or sets \\
\hline
\texttt{e / e} & two integers (integer division) \\
\hline
\texttt{e \% e} & two integers (division remainder) \\
\hline
\texttt{e~..~e} & two integers \\
\hline
\texttt{e in e} & first is any CXL value, second is set \\
\hline
\texttt{e not in e} & first is any CXL value, second is set \\
\hline
\texttt{e if e else e} & middle \texttt{e} must be a Boolean \\
\hline
\texttt{\^{}e} & an address \\
\hline
\texttt{choose e} & a set \\
\hline
\texttt{min e} & a set \\
\hline
\texttt{max e} & a set \\
\hline
\texttt{cardinality e} & a set \\
\hline
\texttt{keys e} & a dictionary \\
\hline
\texttt{len e} & a dictionary (includes tuple or list) \\
\hline
\texttt{bagsize e} & a bag \\
\hline
\texttt{atLabel e} & atom (corresponding to a label) \\
\hline
\texttt{nametag e} & \texttt{e} must be \texttt{()} \\
\hline
\texttt{processes e} & \texttt{e} must be \texttt{()} \\
\hline
\texttt{\&(lv)} & \texttt{lv} is an lvalue \\
\hline
\texttt{stop lv} & \texttt{lv} is an lvalue \\
\hline
\end{tabular}
\vspace{1em}
